\chapter{Tenses}

%{{{ 现在进行时和一般现在时
\section{现在进行时和一般现在时}
\label{sec:presentcontsim}

\subsection{Case A}

\noindent
使用({\bf state verbs})\ref{sec:stateverbs}表示临时的状态或者持续短时间的情况:\newline
\begin{itemize}
\item {\example Jean stays with us quite often. The children love having her here.}
\item {\example Jean's with us at the moment. The children are loving having her here.}
\end{itemize}

\subsection{Case B}

\noindent
有的动词在描述状态({\bf state})或者表示动作({\bf action})时有不同的含义。%
表示状态的含义下，绝大部情况使用一般现在时: 表示动作的含义下，使用那种%
时态取决于所说的内容。\newline
\smallskip
例子:\newline
\begin{itemize}
\item {\example The new treatment for influenza doesn't appear to work.({\bf appear:%
state = seem})}
\item {\example Modonna is currently appearing in a musical on Broadway.%
\/She often appears in musicals.({\bf appear: action=take apart})}
\item {\example Dou you think it's a good idea?({\bf think:state=about an opinion})}
\item {\example I'm thinking of going in August.\/Your trouble is you think too much.%
({\bf think:action=consider})}
\end{itemize}

\subsection{Case C}

\noindent
一些表示精神状态({\bf mental states})的动词({\bf e.g. {\color{word}find, realise, regret, think,%
understand}})可以使用\emph{现在进行时进}行强调\emph{近期思考的某些东西}或者\emph{没有想明白存在困惑的东西}。\par

\noindent
{\bf consider}在表示完全想明白的时候只能用现在进行时\newline
一些动词({\bf e.g. {\color{word}agree, believe, know prefer, conclude}})在表示偏爱({\bf preferences})和{\bf mental state}时只能用现在进行时\newline
\smallskip
例子:\newline

\begin{itemize}
\item {\example I regret that the company will have to be sold.(= I have made the decision%
and I am sorry about it)}
\item {\example I'm regretting my decision to give her the job.(= I am increasingly aware that it was the wrong decision)}
\item {\example He's considering taking early retirement.(Not He considrs taking early retirement.)}
\item {\example I believe you now.(Not I'm believing you now.)}
\end{itemize}

\subsection{Case D}



%}}}
\section{一般过去时和现在完成时}

\section{过去进行时和一般过去时}

\section{过去完成时和一般过去时}

\section{现在完成进行时和现在完成时}

\section{过去完成进行时, 过去完成时, 过去进行时}

\section{现在和过去}
